---
title: "Prudential Data Wrangling"
author: "Francia Moscoso"
date: "April 15, 2016"
output: html_document
---
**Loading Libraries**
```{r LoadLib, message=F, warning=F}
library(dplyr)     
library(corrplot) 
library(ggplot2)
library(Amelia)
```

**Loading Data Sets**
```{r loadDiamonds, comment="", echo=TRUE}
# Working Directory
setwd("~/SprintboardProject/PrudentialIns")  

# Load raw data to 'train' and 'test' repositories
train <- read.csv("./DataSets/train.csv", header = TRUE)
test <-  read.csv("./DataSets/test.csv", header = TRUE)

```


**Read training data set dimension**
```{r comment="", echo=TRUE}
dim(train)
```


**Evaluate missing data**
```{r comment="", echo=TRUE}
missmap(train, main = "Missing values vs observed")
# ---------------------------- To check missing values by subsets -----------
#Id, Product_Info_1-7, Ins_age, Ht, Wt, BMI
#missmap(subset(train,select=c(1:12)),   main = "Missing values vs observed")
#Employment_Info_1-6
#missmap(subset(train,select=c(13:18)),  main = "Missing values vs observed") 
#InsuredInfo_1-6    InsuredInfo_7 is in the next block
#missmap(subset(train,select=c(19:24)),  main = "Missing values vs observed")
#Insurance_History_1-9 - THere is not Insurance_History-6 but InsuredInfo_7
#Missing Data:Insurance_History_5
#missmap(subset(train,select=c(25:33)),  main = "Missing values vs observed")
#Family_Hist_1-5   
#missmap(subset(train,select=c(34:38)),  main = "Missing values vs observed")
#Medical_History_1-41
#missmap(subset(train,select=c(39:59)),  main = "Missing values vs observed")
#missmap(subset(train,select=c(60:79)),  main = "Missing values vs observed")
#Medical_Keyword_1-48
#missmap(subset(train,select=c(80:100)), main = "Missing values vs observed")
#missmap(subset(train,select=c(101:127)),main = "Missing values vs observed")
#Response
#missmap(subset(train,select=c(128:128)),main = "Missing values vs observed")
```

**Ten columns with missing data:**<br>
Insurance_History_5, Family_Hist_2 to Family_Hist_5, Medical_History_1, Medical_History_10,Medical_History15,Medical_History24,Medical_History32

**Percentage of missing data**
```{r comment="", echo=TRUE}
#Number of rows in training data set
TotRow <- nrow(train) 

train %>% filter(is.na(Insurance_History_5)) %>% count()/TotRow
train %>% filter(is.na(Family_Hist_2)) %>% count()/TotRow
train %>% filter(is.na(Family_Hist_3)) %>% count()/TotRow
train %>% filter(is.na(Family_Hist_4)) %>% count()/TotRow
train %>% filter(is.na(Family_Hist_5)) %>% count()/TotRow
train %>% filter(is.na(Medical_History_1)) %>% count()/TotRow
train %>% filter(is.na(Medical_History_10)) %>% count()/TotRow
train %>% filter(is.na(Medical_History_15)) %>% count()/TotRow
train %>% filter(is.na(Medical_History_24)) %>% count()/TotRow
train %>% filter(is.na(Medical_History_32)) %>% count()/TotRow

#Note: Function 'table' does not give you the number of 'NAs' so I count them with function 'is.na'.
#Function 'summary' shows the number of NA's

```
<br>
**The following columns have significant missing data (>30%) so we should discard them in the analysis:**<br>
Insurance_History_5 (42.76%)<br>
Family_Hist_2(48.25%)<br>
Family_Hist_3(57.66%)<br>
Family_Hist_3(32.30%)           Should this variable be discarded???<br>
Family_Hist_5(70.41)<br>
Medical_History_10(99.06%)<br>
Medical_History_15(75.10%)<br>
Medical_History_24(93.59%)<br>
Medical_History_32(98.13%)<br>


tempo1 <- with(train, table(Ins_Age, Id))
<br>
<br>
<br>